\documentclass[11pt]{article}
\usepackage{hyperref} % allows for clickable urls.

% These 3 are for a title page.
\title{My \LaTeX\ Document}
\author{Nathan Ueda}
\date{\today} % You could manually put something, or automaticall have it update using \today.

\begin{document}
\tableofcontents % Creates a table of contents
\maketitle % Needed to put the title page info in.
    This will produce \textit{italized} text.

    This will produce \textbf{bold} text.

    This will produce \textsc{small caps} text.

    This will produce \texttt{typewriter font} text.

    Please visit Michelle Krummel's website at \url{http://michellekrummel.com}

    Please visit Michelle Krummel's website at \href{http://michellekrummel.com}{My Website}
    
    \vspace{1cm}

    Please excuse my dear aunt Sally.

    Please excuse my \begin{large} dear aunt Sally \end{large}. % Makes dear aunt Sally larger.

    Please excuse my \begin{Large} dear aunt Sally \end{Large}. 

    Please excuse my \begin{huge} dear aunt Sally \end{huge}.

    Please excuse my \begin{Huge} dear aunt Sally \end{Huge}.

    Please excuse my \begin{normalsize} dear aunt Sally \end{normalsize}. % Same a the first line.
    
    Please excuse my \begin{small} dear aunt Sally \end{small}. % Going smaller.

    Please excuse my \begin{scriptsize} dear aunt Sally \end{scriptsize}. 

    Please excuse my \begin{tiny} dear aunt Sally \end{tiny}. 

    \vspace{1cm}


    \begin{center}
        This line is centered.
    \end{center}

    \begin{flushleft}
        This line is left justified.
    \end{flushleft}

    \begin{flushright}
        This line is right justified.
    \end{flushright}
    % Putting \section*{Linear Functions} would make it not numbered.
    \section{Linear Functions} % Creating a section (bolded, larger font size, and numbered).
    \subsection{Slope-Intercept Form}
    \subsubsection{Example 1}
    \subsubsection{Example 2}
    \subsection{Standard Form}
    \subsection{Point-Slope Form}
    \section{Quadratic Functions}
    \subsection{Vertex Form}
    \subsection{Standard Form}
    \subsection{Factored Form}
\end{document}